Geometrization of characters of tori over non-Archimedean local fields

### 2013-08-07 shanghai.tex
bounded changes

%%%% Some Named Categories

%%%% Functors

@@

\newcommand{\cdef}[1]{{{\color{cyan}#1}\index{#1}}} 
\newcommand{\sheafHom}{{\mathscr{H}\hskip-4pt{\it o}\hskip-2pt{\it m}}}
\newcommand{\abs}[1]{{\vert #1 \vert}}
\newcommand{\ceq}{{\, :=\, }}
\newcommand{\tq}{{\ \vert\ }}
\newcommand{\iso}{{\ \cong\ }}
\newcommand{\obj}{{\text{obj}\, }}
\newcommand{\Gm}[1]{\mathbb{G}_{\hskip-1pt\textbf{m},#1}}
\newcommand{\GN}[1]{\mathswab{#1}}
\newcommand{\bGN}[1]{{\bar{\mathswab{#1}}}}
\newcommand{\TT}{\underline{T}}
\newcommand{\TL}{\underline{T_L}}
\newcommand{\invlim}[1]{\lim\limits_{\overleftarrow{#1}}}
\newcommand{\dirlim}[1]{\lim\limits_{\overrightarrow{#1}}}
\newcommand{\limit}[1]{\mathop{\textsc{lim}}\limits_{#1}}
\newcommand{\colimit}[1]{\mathop{\textsc{colim}}\limits_{#1}}
\newcommand{\cs}[1]{{\mathcal{#1}}}
\newcommand{\gcs}[1]{{\mathcal{\bar #1}}}
\newcommand{\dualgcs}[1]{\gcs{#1}^\dagger}
\newcommand{\dualcs}[1]{\cs{#1}^\dagger}
\newcommand{\CS}{{\mathcal{C\hskip-1.8pt S}}}
\newcommand{\GC}{{\mathcal{G\hskip-0.8pt C}}}
\newcommand{\CSiso}[1]{\CS(#1)_{/\textit{iso}}}
\newcommand{\CSbiso}[1]{\CS_0(#1)_{/\text{iso}}}
\newcommand{\CE}{{\mathcal{C\hskip-1.8pt E}}}
\newcommand{\Lgroup}[1]{{\,^L\hskip-1pt{#1}}}
\newcommand{\dualgroup}[1]{{\check{#1}}}
\newcommand{\Lang}{{\operatorname{Lang}}}
\newcommand{\image}{{\operatorname{im}}}
\newcommand{\Weil}[1]{\mathcal{W}_{#1}}

@@

%\subsection*{Pull-back of character sheaves}\label{subsection:pullback}

@@

Consider the short exact sequence in the category of smooth group
schemes, locally of finite type over $\Fq$, defining the component
group scheme for $G$:
\begin{equation}\label{eq:pi-2}
\begin{tikzcd}
0 \rar & G^0 \rar & G \rar & \pi_0(G) \rar & 0.
\end{tikzcd}
\end{equation}
Since $\pi_0(G)$ is an Abelian group scheme, smooth (in fact, etale) and locally of finite type over $\Fq$, 
it follows from Proposition~\ref{prop:pullback} that \eqref{eq:pi-1} defines a sequence of functors
\[
\begin{tikzcd}
\CS(0) \rar & \CS(\pi_0(G)) \rar & \CS(G) \rar & \CS(G^0) \rar & \CS(0)
\end{tikzcd}
\]
which induces, upon passage to Picard groups, a sequence of group homomorphisms 
\begin{equation}\label{eq:pi-1}
\begin{tikzcd}
\CSiso{0} \rar & \CSiso{\pi_0(G)} \rar & \CSiso{G} \rar & \CSiso{G^0} \rar & \CSiso{0}.
\end{tikzcd}
\end{equation}
It is easy to see that $\CSiso{0}$ is trivial. In this paper we will find $\CSiso{G^0}$ and $\CSiso{\pi_0(G)}$ under the hypothesis that $\pi_0(G)$ is geometrically finitely generated; the snake lemma then allows us to find $\CSiso{G}$.

\section{Bounded character sheaves}

In this section we describe full subcategory of $\CS(G)$, 
called the category of bounded character sheaves on $G$ and denoted by $\CS_b(G)$, 
which will illuminate the nature of $\CS(G)$ and will also play a role in the arguments later in this paper.

Consider the category $\GC(G)$ of finite etale covers of $G$ that are also morphisms of abelian group schemes.
Recall that we fixed an algebraic closure $\bFq$ of $\Fq$ long ago; 
let ${\bar e} : \Spec{\bFq} \to G$ be the geometric point on $G$ obtained by composing $\Spec{\bFq} \to \Spec{\Fq}$ with the identity $e : \Spec{\Fq} \to G$ for $G$.
Let $\ker_{\bar e}$ be the set-valued functor on $\GC(G)$
defined by pull-back along the geometric point ${\bar e} : \Spec{\bFq} \to G$ 
followed by forgetting the structure sheaf and topology; 
thus, if $f : H\to G$ is a finite etale morphism of group schemes, then $\ker_{\bar e}(f)$ is the set underlying 
$\ker{\bar f} = H_{\bar e}$.
Let $\pi_1^\text{gp}(G)$ be the automorphism group of the functor $\ker_{\bar e}$. 
We will see that $\pi_1^\text{gp}(G)$ is a profinite abelian group.
A \cdef{bounded character sheaf on $G$} is a continuous irreducible representation of $\pi_1^\text{gp}(G)$. 
Let $\CS_b(G)$ be the monoidal category of irreducible continuous $\ell$-adic representations of $\pi_1^\text{gp}(G)$.

\begin{proposition}
 $G\mapsto \pi_1^\text{gp}(G)$ is a functor from group schemes over $\Fq$ to profinite abelian groups, and .....
\end{proposition}

\begin{proof}
The category $\GC(G)$, together with the set-valued functor $\ker_{\bar e}$ satisfy conditions (G1) through (G6) appearing in \cite[Exposé V, \S 4, p. 118-119]{SGA1a}.
\end{proof}

@@

\begin{proposition}\label{prop:connected-1}
  If $G$ is a geometrically connected commutative algebraic group over $\Fq$ then
  \[
  t_{G} : \CSiso{G} \to \Hom_\text{grp}(G(\Fq),\EEx),
  \]
  is an isomorphism of groups.
\end{proposition}

\begin{proof}
  We will prove this proposition by reducing it to the functions--sheaves dictionary
  \cite{Laumon}*{1.1}. The main point of this proof will therefore be to show that,
  {\it since $G$ is geometrically connected}, every character sheaf on $G$ descends to
  a local system on $G$ satisfying the analogue of \ref{CS.1} on $G$.

  First, observe that the forgetful functor $(\gcs{L},\mu,F) \mapsto (\gcs{L},F)$
  sends character sheaves on $G$ to Weil local systems on
  $G$ \cite{Deligne:Weil2}*{1.1.10} (by a Weil local system on $G$ we
  mean a Weil sheaf on $G$ which is a local system on $\bG$).
  While is it not true that all Weil local systems on $G$
  descend to sheaves on $G$, those that appear in the image of the
  forgetful functor from character sheaves do.

  To see why this is so, consider the category \cdef{$\CS_0(G)$} of
  pairs $(\cs{L}_0,\mu_0)$ where $\cs{L}_0$ is a local system on $G$
  and $\mu_0: m^*\cs{L}_0 \to \cs{L}_0 \tight{0}{\boxtimes}{0} \cs{L}_0$ satisfies
  condition \ref{CS.1} adapted to sheaves on $G$; maps in $\CS_0(G)$
  are defined by the second part of condition \ref{CS.2}, {\it mutatis mutandis}.
  \David{This section should be modified once we're done with the section on bounded character sheaves}
  Let $b : \bG \to G$ be base change
  (pull-back of $G\to \Spec{\Fq}$ along $\Spec{\bFq} \to \Spec{\Fq}$).
  The proof of Proposition~\ref{prop:pullback} adapts
  (simplifies, in fact) to show that $b^* : \CS_0(G) \to \CS(G)$ is a
  monoidal functor. This functor is fully faithful; see
  \cite{SGA7.2}*{Expos\'e XIII} and \cite{BBD}*{Prop. 5.2.1}.  We will
  show that $b^*$ is essentially surjective.

@@

>>>>

@@

\newcommand{\cdef}[1]{{{\color{cyan}#1}\index{#1}}} 
\newcommand{\sheafHom}{{\mathscr{H}\hskip-4pt{\it o}\hskip-2pt{\it m}}}
\newcommand{\abs}[1]{{\vert #1 \vert}}
\newcommand{\ceq}{{\, :=\, }}
\newcommand{\tq}{{\ \vert\ }}
\newcommand{\iso}{{\ \cong\ }}
\newcommand{\obj}{{\text{obj}\, }}
\newcommand{\Gm}[1]{\mathbb{G}_{\hskip-1pt\textbf{m},#1}}
\newcommand{\GN}[1]{\mathswab{#1}}
\newcommand{\bGN}[1]{{\bar{\mathswab{#1}}}}
\newcommand{\TT}{\underline{T}}
\newcommand{\TL}{\underline{T_L}}
\newcommand{\invlim}[1]{\lim\limits_{\overleftarrow{#1}}}
\newcommand{\dirlim}[1]{\lim\limits_{\overrightarrow{#1}}}
\newcommand{\limit}[1]{\mathop{\textsc{lim}}\limits_{#1}}
\newcommand{\colimit}[1]{\mathop{\textsc{colim}}\limits_{#1}}
\newcommand{\cs}[1]{{\mathcal{#1}}}
\newcommand{\gcs}[1]{{\mathcal{\bar #1}}}
\newcommand{\dualgcs}[1]{\gcs{#1}^\dagger}
\newcommand{\dualcs}[1]{\cs{#1}^\dagger}
\newcommand{\CS}{{\mathcal{C\hskip-1.8pt S}}}
\newcommand{\GC}{{\mathcal{G\hskip-0.8pt C}}}
\newcommand{\CSiso}[1]{\CS(#1)_{/\textit{iso}}}
\newcommand{\CSbiso}[1]{\CS_0(#1)_{/\text{iso}}}
\newcommand{\CE}{{\mathcal{C\hskip-1.8pt E}}}
\newcommand{\Lgroup}[1]{{\,^L\hskip-1pt{#1}}}
\newcommand{\dualgroup}[1]{{\check{#1}}}
\newcommand{\Lang}{{\operatorname{Lang}}}
\newcommand{\image}{{\operatorname{im}}}
\newcommand{\Weil}[1]{\mathcal{W}_{#1}}
\newcommand{\Loc}{{\operatorname{Loc}}}

@@

\section{Pull-back of character sheaves}\label{subsection:pullback}

@@

Consider the short exact sequence in the category of smooth group
schemes, locally of finite type over $\Fq$, defining the component
group scheme for $G$:
\begin{equation}\label{eq:pi-2}
\begin{tikzcd}
0 \rar & G^0 \rar & G \rar & \pi_0(G) \rar & 0.
\end{tikzcd}
\end{equation}
Since $\pi_0(G)$ is an Abelian group scheme, smooth (in fact, etale) and locally of finite type over $\Fq$, 
it follows from Proposition~\ref{prop:pullback} that \eqref{eq:pi-1} defines a sequence of functors
\[
\begin{tikzcd}
\CS(0) \rar & \CS(\pi_0(G)) \rar & \CS(G) \rar & \CS(G^0) \rar & \CS(0)
\end{tikzcd}
\]
which induces, upon passage to Picard groups, a sequence of group homomorphisms 
\begin{equation}\label{eq:pi-1}
\begin{tikzcd}
\CSiso{0} \rar & \CSiso{\pi_0(G)} \rar & \CSiso{G} \rar & \CSiso{G^0} \rar & \CSiso{0}.
\end{tikzcd}
\end{equation}
It is easy to see that $\CSiso{0}$ is trivial. In this paper we will find $\CSiso{G^0}$ and $\CSiso{\pi_0(G)}$ under the hypothesis that $\pi_0(G)$ is geometrically finitely generated; the snake lemma then allows us to show
\[
\CSiso{G} \iso \Hom(G(\Fq),\EE^\times).
\]

\section{Bounded character sheaves and finite character sheaves}\label{sec:bounded}

 In this section we describe two full subcategories of $\CS(G)$
 which will illuminate some features of $\CS(G)$ and also play a role in some arguments below.

 Let $\CS_0(G)$ be the category of pairs $(\cs{L}_0,\mu_0)$ 
where $\cs{L}_0$ is a constructible $\ell$-adic sheaf on $G$, 
which is a rank-$1$ local system on each connected component of $G$, 
equipped with an isomorphism $\mu_0 : m^* \cs{L}_0 \to \cs{L}_0 \boxtimes \cs{L}_0$ 
satisfying the analogue of Condition~\ref{CS.1} on $G$; 
morphisms in $\CS_f(G)$ are defined as in (the second part of) Condition~\ref{CS.2}. 
This is the category of \cdef{bounded character sheaves} on $G$.

Let $b_G : {\bar G} \to G$ be the pull-back of $\Spec{\bFq} \to \Spec{\Fq}$ along $G\to \Spec{\Fq}$.
If $(\cs{L}_0,\mu_0)$ is bounded character sheaf then $b_G^* \cs{L}_0$ comes equipped with an isomorphism $F : \Frob_G^* b_G^*\cs{L}_0 \to b_G^*\cs{L}_0$ which is compatible with $b_G^* \mu_0$, in the sense of Condition~\ref{CS.3}.
Thus, base change gives us a functor $b_G^* : \CS_f(G) \to \CS(G)$.
This functor is fully faithful; see \cite{SGA7.2}*{Expos\'e XIII} and \cite{BBD}*{Prop. 5.2.1}.

To define the category of finite character sheaves we must work a bit harder.
Consider the following category $C(G)$:
an object in $C(G)$ is a pair $(f,\psi)$ where: $f : H\to G$ is an isogeny (a finite, surjective, etale, morphism of commutative group $\Fq$-schemes) for which the action of $\Gal(\bFq/\Fq)$ on the etale group scheme $\ker f$ is trivial, and $\psi : \ker f\to \Aut(V)$ is a representation on a finite-dimensional $\EE$-vector space $V$;
a map $(f,\psi) \to (f',\psi')$ in $C(G)$ is a pair $(\varphi,T)$ 
where $\varphi$ is a morphism of schemes such that $f' = f\circ \varphi$
and $T : V\to V'$ is a linear transformation equivariant 
for the action of $\ker f'$ on $V'$ by $\psi'$ 
and the action of $\ker f'$ on $V$ by $\psi \circ \varphi$.
%
We say that $(\varphi,T)$ in $C(G)$ is a weak isomorphism if $T$ is an isomorphism of vector spaces. Let $C(G)[W^{-1}]$ be the localization of $C(G)$ at weak isomorphisms.
Now, let $C_1(G)$ be the subcategory of $C(G)$ such that $\psi$ is a one-dimensional representation
and let $\CS_f(G)$ be the localisation of $C_1(G)$ at weak isomorphisms. This is the category of \cdef{finite character sheaves} on $G$.

\begin{proposition}\label{prop:bounded}
 $\CS_f(G)$ is (equivalent to) a full subcategory of $\CS_0(G)$.
\end{proposition}

\begin{proof}
 To prove the proposition we exhibit a fully faithful monoidal functor $L_G : \CS_f(G) \to \CS_0(G)$.
 %
 We will do this by constructing a faithful monoidal functor $L : C_1(G) \to \CS_0(G)$ 
 such that ${\bar L}(\varphi,T)$ is an isomorphism precisely when $(\varphi,T)$ is a weak isomorphism. 
 Factoring along $C_1(G) \to \CS_0(G)$ will produce the full and faithful monoidal functor we seek.

 We start by putting a tensor category structure on $C(G)$. 
 Let $(f,\psi)$ and $(f',\psi')$ be objects in $C(G)$. 
 The category of isogenies to $G$ admits products: 
 write $f\times_G f' : H\times_G H' \to G$ for the product of $f : H\to G$ and $f' : H'\to G$. 
 Since $\ker(f\times_G f') = (\ker f)\times (\ker f')$, 
 the tensor product of the representations $\psi : \ker f\to \Aut(V)$ and $\psi' : \ker f'\to \Aut(V')$ 
 is the representation $\psi \otimes\psi' :  \ker(f\times_G f') \to \Aut(V\otimes V')$. 
 This allows us to set $(f,\psi)\otimes(f',\psi') \ceq (f\times_G f' ,\psi\otimes\psi')$. 
 The same fact makes sense of $(f,\psi)\oplus(f',\psi')\ceq (f\times_G f' ,\psi\oplus\psi')$. 
 The dual of $(f,\psi)$ is $(f,\psi)^\vee \ceq (f,\psi^\vee)$ 
 where $\psi^\vee : \ker f \to \Aut(V^\vee)$ and $V^\vee = \Hom_\text{vec}(V,\EE)$. 
 The verification that these operations make $C(G)$ a tensor category is routine.

  It is also a matter of routine to verify that every morphism of group schemes $G'\to G$ 
  induces a monoidal functor $C(G) \to C(G')$ by base-change along $G'\to G$ ({\it cf.}, Proposition~\ref{prop:pullback}); 
  indeed, the pull-back of $(f,\psi)$ along any morphism $m : G'\to G$ of group schemes 
  can be read off the short exact sequence obtained by pulling back along $m$. 
  Taking the case when $m$ is the multiplication morphism $m : G\times G\to G$, 
  and using the tensor category structure above, 
  we see that the pull-back of $(f,\psi)$ along $m$ is canonically isomorphic, in $C_1(G\times G)$, to $(f,\psi)\boxtimes(f,\psi)$.

 Now we introduce a faithful functor $L : C(G) \to \Loc(G)$ to the category of local systems on $G$.
 For any object $(f,\psi)$ in $C(G)$, let $L(f,\psi)$ be the $\psi$-isotypic component of $f_* V_H$, 
 where $V_H$ refers to $V$ as a constant sheaf on $H$. 
 Note that we may identify the stalk $(f_* V_H)_{\bar g}$ of $f_* V_H$ at a geometric point ${\bar g}$ on $G$ 
 with the $\EE$-vector space $\Hom_\text{set}(\abs{f^{-1}({\bar g})},V)$ 
 and the stalk $L(f,\psi)_{\bar g}$ of $L(f,\psi)$ at a geometric point ${\bar g}$ on $G$ 
 with the $\EE$-vector space consisting of those functions $s: \abs{f^{-1}({\bar g})} \to V$ such that 
 $s(a\cdot {\bar h}) = \psi(a)(s({\bar h}))$ for all $a\in \ker f$ and for all ${\bar h} \in f^{-1}({\bar g})$.
 Since $L(f,\psi)$ is trivialized by $f$, it is a local system on $G$.
 For any map $(\varphi,T)$ in $C(G)$, let $L(\varphi,T) : L(f,\psi) \to L(f',\psi')$ be the homomorphism of local systems defined 
 %at geometric points $L(\varphi,T)_{\bar g} : L(f,\psi)_{\bar g} \to L(f',\psi')_{\bar g}$ 
 by $s \mapsto s' \ceq T\circ s\circ \varphi$. 
 This defines a monoidal functor $L$ from $C(G)$ to $\Loc(G)$. 
 This functor commutes with pull-back along any morphism of group schemes.

 Now consider the localization $C(G)[W^{-1}]$ of $C(G)$ at weak isomorphisms.
 Morphisms in $C(G)[W^{-1}]$ are simple to describe because category $C(G)$ 
 admits a calculus of left fractions\footnote{See {\tt http://ncatlab.org/nlab/show/calculus+of+fractions}.} for weak isomorphisms: 
 every isomorphism in $C(G)$ is a weak isomorphism; 
 push-outs exist in $C(G)$ and the push-out of a weak isomorphism is a weak isomorphism; 
 and weak isomorphisms enjoy the left-cancellation property. 
 It follows that a morphism in $C(G)[W^{-1}]$ is the equivalence class of 
  \[
   \begin{tikzcd}
   (f,\psi) \arrow{r}{(\varphi_1,T_1)} & (f_1,\psi_1) & \arrow[swap]{l}{(\varphi'_1,T'_1)} (f',\psi')
   \end{tikzcd}
  \]
 where $(\varphi',T') : (f,\psi) \to (f',T')$ is any map in $C(G)$ 
 and $(\varphi'_1,T'_1) : (f_1,\psi_1) \to (f',\psi')$ is a weak isomorphism; 
 this morphism is commonly denoted by $(\varphi_1,T_1)^{-1}\circ (\varphi'_1,T'_1)$. 
 %The equivalence relation identifies $(\varphi_1,T_1)^{-1}\circ (\varphi'_1,T'_1)$ 
 % with $(\varphi_2,T_2)^{-1}\circ (\varphi'_2,T'_2)$ if there are maps 
 %$(f_1,\psi_1)\to (f_0,\psi_0)$ and $(f_2,\psi_2)\to (f_0,\psi_0)$ making the following diagram commute
 %\[
 %  \begin{tikzcd}
 %  & (f_1,\psi_1) \arrow{d} & \\
 %  (f,\psi) \arrow{ur}{(\varphi_1,T_1)} \arrow{dr}{(\varphi_2,T_2)} & (f_0,\psi_0)  & \arrow[swap]{ld}{(\varphi'_2,T'_2)} \arrow[swap]{lu}{(\varphi'_1,T'_1)} (f',\psi')\\
 %  & (f_2,\psi_2) \arrow{u} & \\
 %  \end{tikzcd}
 %\]
 %where $(f',\psi') \to (f_0,\psi_0)$ is a weak isomorphism.

 Observe that $L$ takes weak isomorphisms in $C(G)$ to isomorphisms in $\Loc(G)$. To see this, let $(\varphi,T) : (f,\psi)\to (f',\psi')$ be a weak isomorphism, where $f:H\to G$ and $f':H'\to G$ as above. Since $T$ is an isomorphism, we may replace $V'$ with $V$ and $T$ with $\id_V$, without loss of generality. Then the equivariance condition on $T$ becomes $\psi' = \psi\circ \varphi$ on the finite etale group scheme $\ker f'$. Since $f' = f \circ \varphi$ and $f$ and $f'$ are etale covers, it follows that $\varphi$ is also an etale cover. It follows that $\varphi : H'\to H$ admits a section $\varphi' : H \to H'$, which provides the inverse to $L(\varphi,T) : L(f,\psi) \to L(f',\psi')$, above. It is also clear that if $L(\varphi,T)$ is an isomorphism of local systems, then $T$ must be an isomorphism of vector spaces, whence $(\varphi,T)$ is a weak isomorphism: $W$ is saturated.

 Since $L : C(G) \to \Loc(G)$ takes weak isomorphisms to isomorphisms,
 it factors (uniquely!) through the localisation functor $C(G) \to C(G)[W^{-1}]$ 
 to define a faithful functor $L_{W} : C(G)[W^{-1}] \to \Loc(G)$. 
 Since $W$ is saturated, the functor $L_{W} : C(G)[W^{-1}] \to \Loc(G)$ is full. 
 %
 Finally, we are ready to exhibit the full functor $L_G: \CS_b(G) \to \CS_0(G)$ promised above. 
 If $(f,\psi)$ in an object in $C_1(G)$ then, as we have already seen, 
 $m^*L(f,\psi) \iso L(f,\psi) \boxtimes L(f,\psi)$ in $C_1(G\times G)$, canonically.
 It follows immediately that 
  \[
  L_G  \ceq  L_{W}\vert_{\CS_b(G)} : \CS_b(G) \to \CS(G)
  \]
 is a fully faithfull monoidal functor, completing the proof.
\end{proof}

\Clifton{I'll address this point in the next section: "Because $\Gal(\bFq/\Fq)$ acts trivially on $\Aut({\bar f})$, the local system
 ${\bar L}_G(f,\psi)\ceq b_G^* L(f,\psi)$ comes equipped with a canonical isomorphism 
 $F : \Frob_G^* {\bar L}_G(f,\psi) \to {\bar L}_G(f,\psi)$ of constructible sheaves on ${\bar G}$."}

@@

\begin{proposition}\label{prop:connected-1}
  If $G$ is a geometrically connected commutative algebraic group over $\Fq$ then 
  the full subcategories $\CS_b(G) \hookrightarrow \CS_0(G) \hookrightarrow \CS(G)$ 
  appearing in Section~\ref{sec:bounded} are equivalences 
  and
  \[
  t_{G} : \CSiso{G} \to \Hom_\text{grp}(G(\Fq),\EEx),
  \]
  is an isomorphism of groups.
\end{proposition}

\begin{proof}
 %Let $G$ be a geometrically connected algebraic group over $\Fq$.
  Observe that the forgetful functor $(\gcs{L},\mu,F) \mapsto (\gcs{L},F)$
  sends character sheaves on $G$ to Weil local systems on
  $G$ \cite{Deligne:Weil2}*{1.1.10} (by a Weil local system on $G$ we
  mean a Weil sheaf on $G$ which is a local system on $\bG$).
  While is it not true that all Weil local systems on $G$
  descend to local systems on $G$, we will see that those that appear in the image of the
  forgetful functor from character sheaves do. 
  Then we will see that these local systems further appear in the image of

@@

\bib{Kamgarpour}{article}{
   author={Kamgarpour, Masoud},
   title={Stacky abelianization of algebraic groups},
   journal={Transform. Groups},
   volume={14},
   date={2009},
   number={4},
   pages={825--846},
%   issn={1083-4362},
%   review={\MR{2577200 (2011b:20136)}},
%   doi={10.1007/s00031-009-9067-8},
}
